Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-29 manuscript.tex
Bring tex file up to date

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[english,man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring},
            pdfkeywords={social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{float}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi

@@

In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
unjustifiably stripped of his vendor cart by municipal officials. His
humiliation led him to set himself on fire in protest to the authoritarian
rule, ultimately leading to his death several days later. His actions served
as a catalyst for the Tunisian Revolution, and one week after his death, the
long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the
country. The events of Tunisia rapidly spread to surrounding countries that
were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya,
and Syria. These mass movements would not have been possible without
efficient interpersonal coordination, both physically and virtually on social
media platforms, such as Twitter. The events of Arab Spring have been
thoroughly discussed within the political science literature
(e.g., Lutterbeck, 2013; Koehler, 2017) but to our knowledge,
the use of Twitter by Syrian citizens has not been investigated.

\hypertarget{social-cohesion}{%
\subsection{Social Cohesion}\label{social-cohesion}}

Real-world collective action is known to bring about a sense of togetherness,
also known as \enquote{collective effervescence} (Durkheim, 1995). This
feeling of being a part of something larger than oneself leads individuals
to act in ways that would not have on their own. Being overcome with this
feeling is known to lead to violence (Collins, 2009; Spaaij, 2014).
While feelings of social connection may lead to violence, increased exposure
to violence can result in feelings of social cohesion. Gilligan, Pasquale, and Samii (2014)
found that exposure to fatal wartime violence resulted in increased prosocial
motivations, including cooperative behaviors, feelings of trust, and overall
community-level social cohesion. Just as real-world social cohesion can be
quantified, the same is true for online cohesion. Strategic communication on
social media in the form of social cohesion of language can lead to real-world
social change, and exposure to real-world violence could result in social
cohesion in the virtual world. Increased social cohesion is thus potentially
an indicator of increased social organization and mobilization on the ground.

\hypertarget{social-media-as-a-platform-for-mobilization}{%
\subsection{Social Media as a Platform for Mobilization}\label{social-media-as-a-platform-for-mobilization}}

Social media platforms, such as Twitter, offer rapid real-time dissemination
of information. Given its accessibility and proficiency as an information
exchange tool, individuals involved in social movements have taken to them
in conjunction, or in replacement, of real-world social mobilization.
During the 2012 Italian protests for global economic change, the riots in
Rome were mirrored by Twitter activity both on the same day and in the
following days after the protests (Vicari, 2013). Tweeting was
determined to be more effective locally in discussing real-world, real-time
events than traditional mainstream media platforms. As more and more
individuals rely on social media to obtain local news and information, it
becomes increasingly important to understand just how these micro-blogs
reflect real-world action.

\hypertarget{use-of-nonlinear-methods-in-naturally-occurring-data}{%
\subsection{Use of Nonlinear Methods in Naturally Occurring Data}\label{use-of-nonlinear-methods-in-naturally-occurring-data}}

Traditional linear analyses have led to many notable discoveries in the
domains of psychology and political science, but continuous data pose
problems that are not easily overcome with these methods. Events have
historically been conceptualized as linear chains of smaller, sequential
events with one occurrence leading to the next. This notion has been
increasingly replaced by ideas from dynamical systems theory. Rather than
a chain of events, continuous data can be thought of as nested occurrences,
where mutually constrained parts (e.g., citizens, governments, real-world
events, social media platforms) are constantly interacting, leading to
more global behaviors that are larger than the sum of the parts
(Turvey, 2018). When analyzed as dynamical systems, many phenomena
exhibit new nonlinear patterns that were formerly overlooked. Continuous
data subject to linear analyses becomes flattened, and the variability
that is fundamental to these systems and their evolution over time is
ignored. Nonlinear methods provide means for capturing the rich temporal
dynamics and variability that unfold in continuous data.

The primary methods used in the current work is cross-recurrence
quantification analysis (CRQA; Zbilut, Giuliani, \& Webber Jr, 1998) and its offshoot,
windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005).
CRQA has successfully been used to gain a better understanding of many
complex human phenomena, such as human social interactions
(for a review, see Fusaroli, Konvalinka, \& Wallot, 2014) and interpersonal synchrony
(Paxton \& Dale, 2017). We argue that the use of nonlinear methods in
the investigation of political science phenomena will lead to new insights
and development of more robust theories.

@@

Social media has become a primary platform for social movements and
activism across the world, but the extent to which virtual activism
reflects real-world mobilization is still largely unknown. We
conceptualize the physical and virtual movements as a dynamical system,
both constantly interacting and influencing the other. Both real- and
virtual-world collective coordination were powerful tools in the events
of Arab Spring, and are undeniably linked. This study aims to explore
the dynamics of Syrian individuals who took to Twitter to raise
awareness about the events of Arab Spring and bring about mass mobilization.
Using cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998)
and windowed cross-recurrence quantification analysis
(WCRQA; Webber Jr \& Zbilut, 2005), we analyzed the dynamics of social
cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts
of all, positive, and negative real-world events on those respective days.
We hypothesized that the count of all events and the count of negative
events would show high levels of determinism, as this time period was
marked by daily violence which often leads to increased salience. We also
hypothesized that the count of positive events would not show patterns of
determinism, as these events were likely overshadowed by the salient
negative daily occurrences. Using WCRQA, we hoped to identify shifts in the
dynamics of the systems that could then be linked to real world shifts in
conflict frequency. As social cohesion has never been analyzed using
nonlinear methods, the analyses contained herein are largely exploratory.
The goal of this endeavor is to gain a better understanding of how events
of different intensities during times of turmoil may enhance or deter
social cohesion in social media communication, and how social mobilization
may be evident in the dynamic coupling of cohesion and real-world events.

@@

The corpus of tweets used included 697428 Syrian tweets
occurring between March 30, 2012 and June 15, 2012. Using the Twitter
streaming API, servers at the University of Texas at Austin collected
the tweets. The servers were run on a stable (LTS) version of Ubuntu
Linus, 10.04, and were connected directly to the high-bandwidth UT network
maintained by IT services.

Tweets collected contained one or more of the following keywords:
\enquote{syria,} \enquote{syrian,} \enquote{damascus,} \enquote{homs,} \enquote{al-assad,} and \enquote{sunni.} These
keywords were chosen based on the most distinctive terms used in news
articles covering the Arab Spring in Syria at the time. A node.js script
was used to reinitialize the connection to Twitter's servers whenever the
script timed out due to a period of silence. The script requested data from
the API endpoint using basic HTTP authentication (OAuth was optional, at
the time) at \url{https://stream.twitter.com/1.1/statuses/filter.json}, and stored
the data directly to the local hard disk. The tweets were then post-processed
with a Python script to convert the JSON-formatted tweets to tab-separated
files and were then compressed to maximize storage efficiency.

@@

Event data were obtained from the 2012 Integrated Crisis Early Warning
System (ICEWS; Boschee et al., 2015). The event data were first filtered to
remove incomplete and incorrectly formatted data. They were then filtered
to include only events that were directed (i.e., target) at Syria (n = 6300).
To explore the impact of outwardly directed Syrian events, the data were
filtered again to include events that were both directed at (i.e., target)
or directed by (i.e., source) Syria (n = 7990).

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{\label{table-2}CRQA results for source and target data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endhead
DET & 25.246 & 0.001 & *** & 21.148 & 0.127 & & 22.623 & 0.023 & *\tabularnewline
NRLINE & 75.000 & 0.000 & *** & 59.000 & 0.193 & & 64.000 & 0.038 & *\tabularnewline
maxL & 3.000 & 0.423 & & 4.000 & 0.036 & * & 3.000 & 0.370 &\tabularnewline
L & 2.053 & 0.911 & & 2.186 & 0.060 & . & 2.156 & 0.155 &\tabularnewline
ENTR & 0.208 & 0.901 & & 0.510 & 0.047 & * & 0.433 & 0.165 &\tabularnewline
rENTR & 0.300 & 0.802 & & 0.464 & 0.255 & & 0.625 & 0.032 & *\tabularnewline
LAM & 34.262 & 0.003 & ** & 27.705 & 0.035 & * & 24.098 & 0.113 &\tabularnewline
TT & 2.247 & 0.107 & & 2.195 & 0.156 & & 2.100 & 0.360 &\tabularnewline
\bottomrule
\end{longtable}

@@

@@

@@

@@

@@

\leavevmode\hypertarget{ref-paxton2017interpersonal}{}%
Paxton, A., \& Dale, R. (2017). Interpersonal movement synchrony responds to high-and low-level conversational constraints. \emph{Frontiers in Psychology}, \emph{8}, 1135.

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring},
  pdflang={en-EN},
  pdfkeywords={social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{float}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

@@

In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
unjustifiably stripped of his vendor cart by municipal officials. His
humiliation led him to set himself on fire in protest to the authoritarian
rule, ultimately leading to his death several days later. His actions served
as a catalyst for the Tunisian Revolution, and one week after his death,
Zine El Abidine Ben Ali---the longstanding authoritarian president---fled the
country. The events of Tunisia rapidly spread to surrounding countries
also subject to unjust authoritarian rule, including Yemen, Egypt, Libya,
and Syria.

These mass movements would not have been possible without
efficient large-scale coordination, both physically and virtually on social
media platforms. Along with Facebook, Twitter has been credited as essential
to the Arab Spring---both for protesters (as a means to coordinate with one
another and to communicate with the world) and for the government response
(to monitor and track protestors to crack down on dissent) (Comninos, 2011).
The events of Arab Spring have been
thoroughly discussed within the political science literature
(e.g., Lutterbeck, 2013; Koehler, 2017), but to our knowledge,
the direct coupling between Syrian Twitter use and international action
has not been investigated.

\hypertarget{social-cohesion-and-social-mobilization}{%
\subsection{Social Cohesion and Social Mobilization}\label{social-cohesion-and-social-mobilization}}

Real-world collective action is known to bring about a sense of togetherness,
also known as \enquote{collective effervescence} (Durkheim, 1995). This
feeling of being a part of something larger than oneself leads individuals
to act in ways that would not have on their own. Being overcome with this
feeling can lead to violence (Collins, 2009; Spaaij, 2014).
Conversely, increased exposure
to violence can result in positive social cohesion. Gilligan, Pasquale, and Samii (2014)
found that exposure to fatal wartime violence resulted in increased prosocial
motivations, including cooperative behaviors, feelings of trust, and overall
community-level social cohesion.

Just as real-world social cohesion can be
quantified, so can online cohesion. While this can be quantified in many ways,
one kind of cohesion can be found in the similarity in language use on social media.
This implicit or explicit similarity in language use can indicate shared
beliefs, thoughts, and feelings, as has been studied in research on language style
in psycholinguistics and social psychology
(Brennan \& Clark, 1996; Gonzales, Hancock, \& Pennebaker, 2010; Tausczik \& Pennebaker, 2010);
although previous work on language style
has often focused on individuals and small groups, this can be scaled up to examine
massive social-level changes (Fusaroli et al., 2015; Michel et al., 2011).
This kind of massive online social cohesion can lead to real-world
social change.

Combining these separate threads, it is reasonable to expect that real-world actions
and online social interactions would be enmeshed, driving and being driven by
one another. Rather than expecting that only real-world social cohesion would be
driven by real-world action, we would expect interaction between real-world and
virtual dynamics: In this case, exposure to real-world violence could result in social
cohesion in the virtual world. Increased social cohesion is thus potentially
an indicator and a result of increased social organization and mobilization
on the ground.

Social media platforms provide one way of enabling this kind of online social
cohesion by offering distributed information-gathering and real-time information
dissemination. Given its accessibility and proficiency as an information
exchange tool, Twitter has provided individuals involved in social movements
an opportunity to complement or even replace real-world social mobilization.
For example, during the 2012 Italian protests for global economic change, the riots in
Rome were mirrored by Twitter activity both on the day of the protests and in the
days following them (Vicari, 2013). Tweeting was
determined to be more effective locally in discussing real-world, real-time
events than traditional mainstream media platforms. As more and more
individuals rely on social media to obtain local news and information, it
becomes increasingly important to understand just how these micro-blogs
reflect real-world action.

\hypertarget{using-nonlinear-methods-to-capture-complex-relationships}{%
\subsection{Using Nonlinear Methods to Capture Complex Relationships}\label{using-nonlinear-methods-to-capture-complex-relationships}}

Given the hypothesized interrelationship between the real-world
and online actions---and the notorious messiness of naturally occurring
data---it is critical to find appropriate analysis tools that can
identify the complex interconnections.
Traditional linear analyses have led to many notable discoveries in the
domains of psychology and political science, but time series data pose
problems that are not easily overcome with these methods. Events have
historically been conceptualized as linear chains of smaller, sequential
events with one occurrence leading to the next.
Certain kinds of data are relatively well-suited to these analyses,
but messy, complex, variable data from real-world events can pose
challenges from overpowered samples to violation of underlying
statistical assumptions (Paxton \& Griffiths, 2017).

At the same time, the foundational theoretical assumptions of a
linear world has been
increasingly replaced by ideas from dynamical systems theory. Rather than
a chain of events, time series data can be thought of as nested occurrences,
where mutually constrained parts (e.g., citizens, governments, real-world
events, social media platforms) are constantly interacting, leading to
more global behaviors that are larger than the sum of the parts
(Turvey, 2018). Linear analyses flatten these nonlinear patterns in
time series data and ignore the variability
that is fundamental to these systems and their evolution over time.
However, when analyzed as dynamical systems, many phenomena
exhibit new nonlinear patterns that were formerly overlooked.
Nonlinear methods provide means for capturing the rich temporal
dynamics and variability that unfold in time series data.

Although a number of other nonlinear methods exist,
the primary nonlinear method used in the current work is cross-recurrence
quantification analysis (CRQA; Zbilut, Giuliani, \& Webber Jr, 1998) and its offshoot,
windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005).
CRQA has successfully been used to gain a better understanding of many
complex human phenomena, including a variety of human social interactions
(for a review, see Fusaroli, Konvalinka, \& Wallot, 2014).
Much as it has for psychology, we argue that the use of nonlinear methods in
the investigation of political science phenomena will lead to new insights
and the development of more robust theories.

@@

Social media has become a primary platform for social movements and
activism across the world, but the extent to which virtual activism
reflects and drives real-world mobilization is still largely unknown.
In the current work, we
conceptualize the physical and virtual movements as a dynamical system,
both constantly interacting and influencing the other. We aim to study
this by analyzing the real-world events and online social cohesion
during nearly three months of the Arab Spring. Both real- and
virtual-world collective coordination were powerful tools in the events
of the Arab Spring and are undeniably linked. This study aims to explore
the dynamics of Syrian Twitter users, who used the social media platform to raise
awareness about the Arab Spring and bring about mass mobilization.

Using cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998)
and windowed cross-recurrence quantification analysis
(WCRQA; Webber Jr \& Zbilut, 2005), we analyzed the co-evolution of social
cohesion online and real-world events. Specifically, using heterogeneous
data from March 30, 2012, to June 15, 2012, we compared the social cohesion
of Syrian tweets with the counts
of all, positive, and negative real-world events.

We hypothesized that the count of all events and the count of negative
events would show high levels of determinism, as this time period was
marked by daily violence which often leads to increased salience. We also
hypothesized that the count of positive events would not show patterns of
determinism, as these events were likely overshadowed by the salient
negative daily occurrences.
After testing these hypotheses, we then conducted exploratory analyses
to further examine the patterns identified with CRQA. Using WCRQA,
we sought to identify shifts in the
dynamics of the systems that could then be linked to real-world shifts in
conflict frequency.
Through these analyses, our primary goal in the current work was to uncover
(1) how different intensities during times of turmoil may enhance or deter
social cohesion in social media communication and (2) how social mobilization
may be evident in the dynamic coupling of cohesion and real-world events.

An additional focus of the current work is to introduce cross-recurrence
quantification analysis---a longstanding method from physics that has
since become influential in a variety of other fields---to political
science. We do so by providing detailed descriptions of the methods and
providing clear directions about interpretation and significance testing
even with relatively small-\emph{n} or case studies. After demonstrating these
methods' utility with this dataset, we close the paper with specific
suggestions to political scientists interested in incorporating these
methods into their work.

@@

The corpus of tweets used included 697428 Syrian tweets
occurring between March 30--June 15, 2012. Using the Twitter
streaming API, servers at the University of Texas at Austin collected
the tweets. The servers were run on a stable (LTS) version of Ubuntu
Linus (v. 10.04) and were connected directly to the high-bandwidth UT network
maintained by IT services.

Tweets collected contained one or more of the following keywords:
\enquote{syria,} \enquote{syrian,} \enquote{damascus,} \enquote{homs,} \enquote{al-assad,} and \enquote{sunni.} These
keywords were chosen based on the most distinctive terms used in news
articles covering the Arab Spring in Syria at the time. A node.js script
was used to reinitialize the connection to Twitter's servers whenever the
script timed out due to a period of silence. The script requested data from
the API endpoint using basic HTTP authentication (OAuth was optional, at
the time) at \url{https://stream.twitter.com/1.1/statuses/filter.json}, and stored
the data directly to the local hard disk. The tweets were then post-processed
with a Python script to convert the JSON-formatted tweets to tab-separated
files, which were then compressed to maximize storage efficiency.

@@

Event data were obtained from the 2012 Integrated Crisis Early Warning
System (ICEWS; Boschee et al., 2015). The event data were first filtered to
remove incomplete and incorrectly formatted data. They were then filtered
to include only events that were directed at (i.e., \texttt{target}) Syria (\(n = 6300\)).
To explore the impact of outwardly directed Syrian events, the data were
filtered again to include events that were both directed at (i.e., \texttt{target})
or directed by (i.e., \texttt{source}) Syria (\(n = 7990\)).

@@

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{\label{table-2}CRQA results for source and target data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endhead
DET & 25.246 & 0.001 & *** & 21.803 & 0.074 & . & 22.623 & 0.023 & *\tabularnewline
NRLINE & 75.000 & 0.000 & *** & 61.000 & 0.121 & & 64.000 & 0.038 & *\tabularnewline
maxL & 3.000 & 0.423 & & 4.000 & 0.037 & * & 3.000 & 0.370 &\tabularnewline
L & 2.053 & 0.911 & & 2.180 & 0.079 & . & 2.156 & 0.155 &\tabularnewline
ENTR & 0.208 & 0.901 & & 0.499 & 0.064 & . & 0.433 & 0.165 &\tabularnewline
rENTR & 0.300 & 0.802 & & 0.455 & 0.305 & & 0.625 & 0.032 & *\tabularnewline
LAM & 34.262 & 0.003 & ** & 30.328 & 0.016 & * & 24.098 & 0.113 &\tabularnewline
TT & 2.247 & 0.107 & & 2.176 & 0.165 & & 2.100 & 0.360 &\tabularnewline
\bottomrule
\end{longtable}

@@

\leavevmode\hypertarget{ref-brennan1996conceptual}{}%
Brennan, S. E., \& Clark, H. H. (1996). Conceptual pacts and lexical choice in conversation. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{22}(6), 1482.

@@

\leavevmode\hypertarget{ref-comninos2011twitter}{}%
Comninos, A. (2011). \emph{Twitter revolutions and cyber crackdowns}. Association for Progressive Communications.

@@

\leavevmode\hypertarget{ref-fusaroli2015timescales}{}%
Fusaroli, R., Perlman, M., Mislove, A., Paxton, A., Matlock, T., \& Dale, R. (2015). Timescales of massive human entrainment. \emph{PloS ONE}, \emph{10}(4).

@@

\leavevmode\hypertarget{ref-gonzales2010language}{}%
Gonzales, A. L., Hancock, J. T., \& Pennebaker, J. W. (2010). Language style matching as a predictor of social dynamics in small groups. \emph{Communication Research}, \emph{37}(1), 3--19.

@@

\leavevmode\hypertarget{ref-michel2011quantitative}{}%
Michel, J.-B., Shen, Y. K., Aiden, A. P., Veres, A., Gray, M. K., Pickett, J. P., \ldots{} others. (2011). Quantitative analysis of culture using millions of digitized books. \emph{Science}, \emph{331}(6014), 176--182.

\leavevmode\hypertarget{ref-paxton2017finding}{}%
Paxton, A., \& Griffiths, T. L. (2017). Finding the traces of behavioral and cognitive processes in big data and naturally occurring datasets. \emph{Behavior Research Methods}, \emph{49}(5), 1630--1638.

@@

\leavevmode\hypertarget{ref-tausczik2010psychological}{}%
Tausczik, Y. R., \& Pennebaker, J. W. (2010). The psychological meaning of words: LIWC and computerized text analysis methods. \emph{Journal of Language and Social Psychology}, \emph{29}(1), 24--54.
